Bow shocks, bow waves, and dust waves

### 2018-06-03 papers/Papers1234/sec-dust-bow-intro.tex
Write about the stagnant drift solution

Examples of the each of these two behaviors are illustrated in
Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
regime, resulting in periodic ``limit-cycle'' behavior (the parameters
of this model correspond to the yellow ``plus'' symbol labeled ``40''
in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
grain's approach it initially follows an equilibrium drift phase
trajectory (lower left panel) along the \(f\rad - f\drag = 0\)
contour, with a very slight deceleration.  Then, when it reaches the
rip point, \(R = R_\dag\), it suddenly experiences an unbalanced outward
radiation force (blue region of phase space in
Fig.~\ref{fig:phase-space-trajectories}). The grain's inward momentum
carries it to the point \(R\min\), which is only slightly inside
\(R_\dag\), before it is expelled at roughly twice the inflow speed.
However, after moving outward, it finds itself in a drag-dominated
region of phase space (red in the figure), and so recouples to the
inflowing gas stream.  The recoupling is gradual at first, as the
grain's outward motion is slowed and it begins to move inward again,
but is completed suddenly once \(w\) falls below \SI{10}{km.s^{-1}} in
what we term \textit{snap back}. The net result is the grain is back
on the same phase track that it came in on, and so repeats the cycle
indefinitely.

The grain trajectory can be seen to follow a limit cycle, in which

whether or not
the incoming stream velocity lies in drag regime IV
(Table~\ref{tab:fdrag-regimes}) with , which
produces the unstable drift region identified in
Figure~\ref{fig:gas-grain-drag-photoionized}.

>>>>

An examples of each of these two behaviors is illustrated in
Figure~\ref{fig:phase-space-trajectories}.  The left panels show the
case where \(v_\infty = \SI{40}{km.s^{-1}}\), which is in the unstable
regime, resulting in periodic ``limit-cycle'' behavior (the parameters
of this model correspond to the yellow ``plus'' symbol labeled ``40''
in the left panel of Fig.~\ref{fig:existence-dust-wave}).  During the
grain's first approach, it starts to follow a phase trajectory (lower
left panel) along the \(f\rad - f\drag = 0\) contour, corresponding to
equilibrium drift, in which the grain begins to move a few
\si{km.s^{-1}} slower than the gas stream.  Then, when it reaches the
rip point (\(R = R_\dag\), \(w \approx \SI{10}{km.s^{-1}}\)) it suddenly
experiences a large unbalanced outward radiation force (blue region of
phase space in Fig.~\ref{fig:phase-space-trajectories}). The grain's
inward momentum carries it to the point \(\Rmin \approx 0.85 R_\dag\), before
it is expelled at roughly twice the inflow speed.  However, after
moving outward, it finds itself in a drag-dominated region of phase
space (red in the figure), and so recouples to the inflowing gas
stream.  The recoupling initiates gradually, as the grain's outward
motion is slowed and it begins to move inward again, but is completed
suddenly once \(w\) again falls below \SI{10}{km.s^{-1}}, in what we
term \textit{snap back}. The net result is that the grain has returned
to exactly the same phase track that it started in on, and so repeats
the cycle indefinitely.

The right panels of Figure~\ref{fig:phase-space-trajectories} show the
case where the stream velocity is doubled to
\(v_\infty = \SI{80}{km.s^{-1}}\), but all other parameters remain the
same.  At this velocity, the equilibrium drift is stable and so the
grain can achieve a stagnant drift solution, where it is stationary
with respect to the star.  The trajectory during the first approach is
similar to the previous case, except that the overshoot of the rip
point is greater, so that \(\Rmin \approx 0.65 R_\dag\) in this case.  This is
a consequence of the fact that the rip point is closer to the
drag-free turnaround radius (\(R_\dag / R\star\star\) is not so small as in the
lower velocity case), so that the grain inertia is relatively more
important.  A second consequence is that the speed of the initial
expulsion is not so large, being only a little higher than the inflow
velocity (but opposite to it).  The qualitative difference between the
two cases emerges after the first recoupling: instead of the snap back
and endless limit cycle, the grain oscillates about the stagnant drift
radius with ever decreasing amplitude, so that it has come almost to
rest after a few oscillation periods.
